Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-25 Arxiv/main.tex
small edit
fix typos

\noindent \textbf{Sliding Property of $\hexpmech$}
\begin{lem}
\label{lem_sliding}
Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
\end{equation*}

@@

		We denote the normalizer of the probability mass in $\hexpmech(\dataobs)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(\dataobs)})$ as $NL(\dataobs)$:
		\begin{equation*}
		\begin{split}
		LHS 
		  = \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
		& = |r| \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
		\end{split}
		\end{equation*}

@@

		\begin{equation*}
		\begin{split}
		|r|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
		&  \leq |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}

>>>>

\noindent \textbf{Sliding Property of $\hexpmech$}
\begin{lem}
\label{lem_sliding}
Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
\end{equation*}

@@

		We denote the normalizer of the probability mass in $\hexpmech(\dataobs)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(\dataobs)})$ as $NL(\dataobs)$:
		\begin{equation*}
		\begin{split}
		LHS 
		  = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
		& = |z| \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
		\end{split}
		\end{equation*}

@@

		\begin{equation*}
		\begin{split}
		|z|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
		&  \leq |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = (\delta' + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}
